---
output: github_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# new.name

An R package that uses the babynames and unisex datasets to help users choose new names using criteria having to do with the letters in the name (e.g., a beginning letter) and/or a year. You will be able to find names that were used in the United States at least five times during that year if you specify a year. More name sets to be added!


## Purpose

There are many reasons people may need a new name. Whether you are trans and looking for a name that better fits your gender identity; naming a new child, pet, company or feature; or even a new artificial intelligence entity, new.name can help! This package uses string manipulation and data wrangling to find subsets of names based on certain characteristics. 
Perhaps you want to choose a new name that starts with certain letters or maybe you want something random. 


## Target

Though it was designed for trans people looking to pick a name popular in their birth year, new.name is also able to be uses anyone!


## Installation

You can install the development version of `new.name` like so:


## Example

Find popular names during a year(y) that starts with a letter(x)

```{r}
new_Names("A",2000)
```
"Alanni"    "Alezander" "Ashunti"
## Example 
Find a random name

```{r random name}
RandomName()
```
Marlowe

## Project Proposal for part III

Work on this same package but add....
