---
title: "newname"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{newname}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(new.name)
```

## Welcome to the new.name package.
The `new.name` package has functions and data sets that are included for their use in finding names. It also loads a variety of other packages when installed. Finding 

There are many reasons people may need a new name. Whether you are trans and looking for a name that better fits your gender identity; naming a new child, pet, company or feature; or even a new artificial intelligence entity, new.name can help! This package uses string manipulation and data wrangling to find subsets of names based on certain characteristics. 
Perhaps you want to choose a new name that starts with certain letters or maybe you want something random. 

Though it was designed for trans people looking to pick a name popular in their birth year, `new.name` is also able to be used for anyone!

One of of the biggest tools in the new.name package is the `new_Names()` function. This function allows a user to find popular names during a year(y) that starts with a letter(x).

```{r}
new_Names("A",2000)
```


If you want to find a random name use the function `RandonName()`

```{r random name}
RandomName()
```

If you arent interested in these functions and want to explore on your own, the new.name package includes a variety of data sets containing data about names. 

This package includes the `babynames`, `unisex`, `spanish_female`, `spanish_male`, and `celeb` data sets. 


The `babynames` data is a commonly known data set first introduced to github by hadley wickham and included in the tidyverse dependency. 

```{r}
head(babynames)
```

The `unisex` data set contains 900 names given to each gender at least one third of the time with a minimum of 100 people with that name.

```{r}
head(unisex)
```

The `spanish_female` data contains 24746 Spanish first names given to current female Spanish residents and newborns birthed in the past 15 years. Cleaned by jvalhondo on github.

```{r}
head(spanish_female)
```

The `spanish_male` data contains 24584 Spanish first names given to current male Spanish residents and newborns birthed in the past 15 years. Cleaned by jvalhondo on github.

```{r}
head(spanish_male)
```


The `celeb` data contains 4557 celebrity names, occupations, roles etc.

```{r}
head(celeb)
```

