---
title: "newname"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{newname}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(new.name)
```

## Welcome to the new.name package.
The `new.name` package has functions and data sets that are included for their use in finding names. It also loads a variety of other packages when installed. Finding 

There are many reasons people may need a new name. Whether you are trans and looking for a name that better fits your gender identity; naming a new child, pet, company or feature; or even a new artificial intelligence entity, new.name can help! This package uses string manipulation and data wrangling to find subsets of names based on certain characteristics. 
Perhaps you want to choose a new name that starts with certain letters or maybe you want something random. 

**install new.name like so:**

`devtools::install_github("mars-ikeda/new.name")`


One of of the biggest tools in the new.name package is the `new_Names()` function. This function allows a user to find popular names during a year(y) that starts with a letter(x).

```{r}
new_Names("A",2000)
```


If you want to find a random name use the function `RandonName()`

```{r random name}
RandomName()
```

If you arent interested in these functions and want to explore on your own, the new.name package includes a variety of data sets containing data about names. 

This package includes the `babynames`, `unisex`, `spanish_female`, `spanish_male`, and `celeb_infor_csv` data sets. 


The `babynames` data is a commonly known data set first introduced to github by hadley wickam. This 
